\documentclass{article}

\usepackage[a4paper]{geometry}

\begin{document}

\section*{Things to Fix:}
NB: There are still comments in the .tex files using my self-styled ``tstk" command that will need to be removed.

\subsection*{Intro Chapter}
\begin{itemize}
	\item Check file for full details.
	\item Ask Susie about whether content from the TFR can be re-used if referenced, as the introduction is very useful and likely to be similar.
	\item David's scaling: important to reconcile content from meeting on 3/2/20
\end{itemize}

\subsection*{Quantum Graphs Chapter}
No major issues, see .tex file for ``tstk" commands and self-comments.

\subsection*{Scalar Equations}
\begin{itemize}
	\item References to Zhikov
	\item Perhaps trim down the chapter, it really only serves as motivation for us and (despite not being written explicitly in his papers) has been done by Zhikov
\end{itemize}

\subsection*{Vector Equations}
\begin{itemize}
	\item $H^1_{\mathrm{curl}}$ inclusion conditions. Have one component, but need the condition on the other two. Have an idea, need to look into proving
	\item $j\sim k$ notation still persists - go through and cross check
\end{itemize}

\subsection*{Example Systems}
\begin{itemize}
	\item 5 Vertex graph system - some numerical results?
	\item Python code for solving graph problems, have written some, seems to work, maybe include something on this if I can get it into a viable solving state soon?
	\item Chevron example could be included but doesn't produce anything interesting
	\item Thick vertex case, justify equations and boundary conditions. Partially done.
	\item Summary (needs link to physical meaning once intro is written)
\end{itemize}

\subsection*{Conclusion}
\begin{itemize}
	\item Check file for details
	\item Need to finish Example Systems chapter for that part of the conclusion
	\item CAN write Scalar \& Vector equations part
\end{itemize}

\end{document}