\section{Appendix: Sobolev spaces associated with the measure $\nu$} \label{app:VertexAnalysis}
Our analysis of $\gradSobQM{\ddom}{\ddmes}$ even provides us with Sobolev functions that are continuous across the vertices.
However we are not encapsulating the effect of introducing coupling constants $\alpha_j$ to the vertices in $\graph$ yet - and to do so we must examine the ``vertex part" $\nu$ of our measure $\dddmes$ and the Sobolev spaces associated with it.
Thankfully, our analysis of the space $\gradSobQM{\ddom}{\nu}$ is short, on account of the fact that $\gradZero{\ddom}{\nu}$ (as a subset of $\ltwo{\ddom}{\nu}^2$) is actually isomorphic to $\complex^N$, where $N=\abs{\vertSet}$ is the number of vertices in the graph $\graph$.
As such, any $\bracs{u,\grad_{\nu}u}\in\gradSob{\ddom}{\nu}$ has $\grad_{\nu}u=0$.

\subsection{Analysis of $\nu$-Gradients of Zero} \label{appS:VertexGradZero}
We begin by defining some quantities that will appear in the proofs of this section.
\begin{definition}[$d$, $\varphi_c$, and $g^j$] \label{def:UsefulObjects}
	Denote
	\begin{align*}
		d &:= \recip{2}\min\clbracs{\norm{v_j-v_k}_2 \ \vert \ v_j,v_k\in\vertSet},
	\end{align*}
	which exists since the graph $\graph$ is assumed finite, and is positive.
	For $c\in\complex$, let $\varphi_c:\reals^2\rightarrow\complex$ be a smooth function such that
	\begin{align*}
		\varphi_c\bracs{0} = 0, 
		\quad \grad\varphi_c\bracs{0} = c,
		\quad \supp\bracs{\varphi_c} \subset B_{d}\bracs{0},
	\end{align*}
	where $B_{d}\bracs{0}$ denotes the ball of radius $d$ centred at the origin.
	Finally, for each $v_j\in\vertSet$ define
	\begin{align*}
		g^j_1\bracs{x} &=
		\begin{cases}
			\bracs{1,0}^\top, & x=v_j, \\
			0, & x\neq v_j. \\
		\end{cases}
		&\quad
		g^j_2\bracs{x} &=
		\begin{cases}
			\bracs{0,1}^\top, & x=v_j, \\
			0, & x\neq v_j. \\
		\end{cases}
	\end{align*}
\end{definition}

We now demonstrate that $\ltwo{\ddom}{\nu}^2$ is isomorphic to $\complex^{2N}$.
\begin{lemma}
	The space $\ltwo{\ddom}{\nu}$ is isomorphic to $\complex^{2N}$.
	Moreover, the collection $\clbracs{g_1^j, g_2^j \ \vert \ v_j\in\vertSet}$ forms a basis of $\ltwo{\ddom}{\nu}^2$.
\end{lemma}
\begin{proof}
	It is sufficient to notice that any $f\in\ltwo{\ddom}{\nu}^2$ is entirely determined by the values it takes at the vertices $v_j$.
	Each of these values is a $\complex^2$-vector, and thus we may define the function
	\begin{align*}
		\iota:\ltwo{\ddom}{\nu}^2 \rightarrow\complex^{2N}, &\quad
		\iota\bracs{f} = \bracs{ f\bracs{v_1}, ..., f\bracs{v_N} }^\top,
	\end{align*}
	where we vertically concatenate the collection of two-vectors $f\bracs{v_j}, v_j\in\vertSet$.
	Clearly $\iota$ is a bijection, and additionally for $f,g\in\ltwo{\ddom}{\nu}$ we have that
	\begin{align*}
		\integral{\ddom}{f\cdot \overline{g}}{\nu} 
		&= \sum_{v_j\in\vertSet} f\bracs{v_j}\cdot\overline{g\bracs{v_j}}
		= \iota\bracs{f}\cdot\overline{\iota\bracs{g}},
	\end{align*}
	so $\iota$ is an isometry.
	Moreover, the preimage of the canonical basis $\clbracs{e_k \ \vert \ k\in\clbracs{1,...,2N}}$ under $\iota$ is the collection $\clbracs{g_1^j, g_2^j \ \vert \ v_j\in\vertSet}$, and hence $\clbracs{g_1^j, g_2^j \ \vert \ v_j\in\vertSet}$ forms a basis of $\ltwo{\ddom}{\nu}^2$.
\end{proof}

We now characterise the set of $\nu$-gradients of zero, $\gradZero{\ddom}{\nu}$, which we find to be the entire space $\ltwo{\ddom}{\nu}^2$.
\begin{prop}[Characterisation of $\gradZero{\ddom}{\nu}$] \label{prop:CharPointMassGradZero}
	We have that $\gradZero{\ddom}{\nu} = \ltwo{\ddom}{\nu}^2$.
\end{prop}
\begin{proof}
	Since $\gradZero{\ddom}{\nu}$ is a closed, linear subspace of $\ltwo{\ddom}{\nu}^2$ by definition, it is sufficient to show that $\gradZero{\ddom}{\nu}$ contains the basis $\clbracs{g_1^j, g_2^j \ \vert \ v_j\in\vertSet}$.
	We demonstrate inclusion of the elements $g^j_1$ (as that of $g^j_2$ is similar).
	Take $c=\bracs{1,0}^{\top}$, fix $v_j\in\vertSet$, and set
	\begin{align*}
		\phi\bracs{x} &= \varphi_c\bracs{x-v_j},
	\end{align*}
	where $\varphi_c$ is as in definition \ref{def:UsefulObjects}.
	Note that $\phi$ is smooth by composition of smooth functions, $\supp\bracs{\phi}\subset B_{d}\bracs{v_j}$, and that $\grad\phi\bracs{x} = \bracs{\grad\varphi_c}\bracs{x-v_j}$.
	Then clearly
	\begin{align*}
		\integral{\ddom}{\abs{\phi}^2}{\nu} = 0,
		&\quad \integral{\ddom}{\abs{\grad\phi - g^j_1}^2}{\nu} = 0.
	\end{align*}
	Hence, one has $g^j_1\in\gradZero{\ddom}{\nu}$.
\end{proof}

\subsection{The Sobolev Space $\gradSobQM{\ddom}{\nu}$} \label{appS:VertexSobSpace}
Given that we now know that $\gradZero{\ddom}{\nu}$ encompasses the whole of $\ltwo{\ddom}{\nu}^2$, we must conclude that our ``Sobolev functions" have zero derivative ($\nu$-)almost-everywhere.
Indeed, proposition \ref{prop:CharPointMassGradZero} gives us the following corollary:
\begin{cory}[Characterisation of $\gradSobQM{\ddom}{\nu}$] \label{cory:CharPointMassSpace}
	We have that $\bracs{u,\tgrad_{\nu}u}\in\gradSobQM{\ddom}{\nu}$ if and only if $u\in\ltwo{\ddom}{\nu}$ and $\tgrad_{\nu}u = 0$ $\nu$-almost everywhere.
\end{cory}
\begin{proof}
	First assume $\bracs{u,\tgrad_{\nu}u}\in\gradSobQM{\ddom}{\nu}$.
	Then $\tgrad_{\nu}u\in\ltwo{\ddom}{\nu}^2$ is an element of $\ltwo{\ddom}{\nu}^2$ by definition and is orthogonal to $\gradZero{\ddom}{\nu}$, but by proposition \ref{prop:CharPointMassGradZero} we know that $\gradZero{\ddom}{\nu}=\ltwo{\ddom}{\nu}^2$, so we must conclude that $\grad_{\nu}u = 0$.
	
	For the converse implication, take smooth ``bump" functions $\psi_j$ for each $v_j\in\vertSet$ with the properties
	\begin{align*}
		\psi_j\bracs{v_j} = 1, 
		\quad \grad\psi_j\bracs{v_j} = -\rmi\qm,
		\quad \supp\bracs{\psi_j} &\subset B_{d}\bracs{v_j}.
	\end{align*}
	(Note that these are just translated versions of the functions $\psi_c$ in definition \ref{def:UsefulObjects} with $c=-\rmi\qm$).
	Then consider the smooth function
	\begin{align*}
		\phi\bracs{x} := \sum_{v_j\in\vertSet} u\bracs{v_j}\psi_j\bracs{x},
		&\quad \grad\phi\bracs{x} = \sum_{v_j\in\vertSet} u\bracs{v_j}\grad\psi_j\bracs{x}.
	\end{align*}
	Then we have
	\begin{align*}
		\integral{\ddom}{\abs{\phi - u}^2}{\nu} &= \sum_{v_j\in\vertSet} \alpha_j\abs{\phi\bracs{v_j} - u\bracs{v_j}}^2 \\
		&= \sum_{v_j\in\vertSet} \alpha_j\abs{ \sum_{v_l\in\vertSet}u\bracs{v_l}\psi_l\bracs{v_j} - u\bracs{v_j} }^2
		= \sum_{v_j\in\vertSet} \alpha_j\abs{u\bracs{v_j}}^2\abs{\psi_j\bracs{v_j}-1}^2 = 0
	\end{align*}
	and
	\begin{align*}
		\integral{\ddom}{\abs{\tgrad\phi - 0}^2}{\nu} 
		&= \sum_{v_j\in\vertSet} \alpha_j\abs{ \sum_{v_l\in\vertSet} u\bracs{v_l}\grad\psi_l\bracs{v_j} + i\qm\psi_l\bracs{v_j} }^2 \\
		&= \sum_{v_j\in\vertSet} \alpha_j\abs{u\bracs{v_j}}^2 \abs{ \grad\psi_j\bracs{v_j} + i\qm\psi_j\bracs{v_j} }^2
		= \sum_{v_j\in\vertSet} \alpha_j\abs{u\bracs{v_j}}^2 \abs{ i\qm - i\qm } = 0.
	\end{align*}
	Thus, the constant sequence $\phi$ is such that
	\begin{align*}
		\phi \lconv{\ltwo{\ddom}{\nu}} u, \quad \tgrad\phi \lconv{\ltwo{\ddom}{\nu}^2} 0,
	\end{align*}
	and thus $\bracs{u,0}\in\gradSob{\ddom}{\nu}$.
\end{proof}
Corollary \ref{cory:CharPointMassSpace} means that the space $\gradSob{\ddom}{\nu}$ is essentially isomorphic to $\complex^N$, namely functions in this space are entirely determined by their values at the vertices, and their gradients are always zero.
This matches our intuitive expectations, as the notion of a gradient (or rate of change) at a point being non-zero implies that there is a small neighbourhood around the point in which we can observe the function values changing, but in the case of a point-mass measure centred on isolated points, this is not the case.